Appendix A: Stochastic simulations of noisy phenomena

### 2017-11-01 appendixA/appendixA.Rmd
drop commented calls

extrafont::loadfonts()
ggplot2::theme_set(hrbrthemes::theme_ipsum_rc())
```

>>>>

## One-time setup
hrbrthemes::import_roboto_condensed()   # One-time use to set up fonts 
d <- read.csv(extrafont:::fonttable_file(), stringsAsFactors = FALSE)
d[grepl("Light", d$FontName), ]$FamilyName <- "Roboto Condensed Light"
write.csv(d, extrafont:::fonttable_file(), row.names = FALSE)

## load fonts (needed each time)
extrafont::loadfonts()
ggplot2::theme_set(hrbrthemes::theme_ipsum_rc())
```
